Stateless Model Checking with Data-Race Preemption Points

### 2016-07-19 oopsla-16/evaluation.tex
cite simsa thesis

% TODO: Fix up this paragraph after preempt-everywhere results come in.
The left half of Table~\ref{tab:drbugs}
breaks down the number and types of bugs found by each test program.
In \mxtest, in which we do not trust the lock implementation's correctness,
% TODO CAMREADY: Fix, SSSMC-ShM finds 2 mx bugs.
\revisionx{SSS-MC-ICB and SSS-MC-DPOR}
found dramatically fewer bugs (just 1)\footnote{
	The one bug SSS-MC found was in a fully-assembler lock implementation. {\tt yield()}'s return value clobbered a value stored in {\tt \%eax}, which could lead to a failure after two repeated contentions. Preempting only on {\tt yield()} (in the contention loop) was sufficient to find the bug.}.
%Intuitively, this is due to our control experiment being able to preempt only on the boundaries of the API which
%Though for many applications of MC, assuming a correct lock implementation is sufficient,
% TODO CAMREADY cite simsa thesis
Though it often suffices to assume correctly-implemented locks,
we consider this strong evidence that new low-level synchronization code must be verified with data-race PPs.
%TODO CAMREADY: Run a mutex expt where "all atomic instrs" are PPs. See how many bugs are missed anyway.
% Wwe re-ran the \mxtest control experiment with \landslide~hard-coded to preempt on any atomic instruction
% (as well as on the mutex API boundaries).
% Still, this smarter configuration for SSS-MC found only 99999999999 bugs of \quicksand's 13.

>>>>

% TODO: Fix up this paragraph after preempt-everywhere results come in.
The left half of Table~\ref{tab:drbugs}
breaks down the number and types of bugs found by each test program.
In \mxtest, in which we do not trust the lock implementation's correctness,
% TODO CAMREADY: Fix, SSSMC-ShM finds 2 mx bugs.
\revisionx{SSS-MC-ICB and SSS-MC-DPOR}
found dramatically fewer bugs (just 1)\footnote{
	The one bug SSS-MC found was in a fully-assembler lock implementation. {\tt yield()}'s return value clobbered a value stored in {\tt \%eax}, which could lead to a failure after two repeated contentions. Preempting only on {\tt yield()} (in the contention loop) was sufficient to find the bug.}.
%Intuitively, this is due to our control experiment being able to preempt only on the boundaries of the API which
%Though for many applications of MC, assuming a correct lock implementation is sufficient,
Though it often suffices to assume correctly-implemented locks \cite{dbug-thesis},
we consider this strong evidence that new low-level synchronization code must be verified with data-race PPs.
%TODO CAMREADY: Run a mutex expt where "all atomic instrs" are PPs. See how many bugs are missed anyway.
% Wwe re-ran the \mxtest control experiment with \landslide~hard-coded to preempt on any atomic instruction
% (as well as on the mutex API boundaries).
% Still, this smarter configuration for SSS-MC found only 99999999999 bugs of \quicksand's 13.
